\Large \bf FlexAlloc: Dynamic Memory Partitioning\\ between the Corevisor and Hostvisor in SeKVM

### 2023-12-24 paper.tex
Somewhat resolved formatting issues, still broken

Although the metadata structs have a much smaller memory footprint than the stage-2 page tables,
we designed and partially implemented a fully generalized dynamic allocation interface that
could be used to support dynamic allocation for all metadata structs which we call the
Dynamic Page Manager (DPM). DPM handles all of the work required to receive and return
memory from the hostvisor allowing other "services" in EL2 to exchange memory with DPM using
a very similiar interface to the alloc_pages and free_pages interface available in EL1. We describe
this interface in detail in Section 4.

@@

In order to make sure that the host can reasonably be expected to find 8x 1MB
contiguous regions when booting a VM, we evaluated how many successful
alloc_pages(1MB) calls could be made before failure. To reproduce our tests,
simply compile host-sekvm-project with the \textit{ALLOC\_STRESS\_TEST} macro defined.
Across our three trails, after booting host SeKVM with the FlexAlloc extension,
we were able to achieve between 7049 and 7054 successful 1MB allocations
from alloc_pages(1MB) calls. Since each VM only needs 8 successful allocations,
we believe that the upperbound on the number of VM's due to potential alloc_pages(1MB)
failures is sufficiently high.

We verified the changes in corevisor's memory footprint by checking the number of
pages owned by the corevisor according to the \textit{el2\_data\-\>s2\_pages} array at key points
throughout the VM boot and destruction processes. On a host running SeKVM without the
FlexAlloc extension, we observed that the Corevisor owned 65549 pages before booting a VM,
while running a VM, and after destroying a VM. On a host running SeKVM with the FlexAlloc
extension, we observed that the Corevisor owned 32768 pages before VM boot, 34817 pages
during the life of the VM, and 32768 pages after destroying the VM. Note that FlexAlloc also
reduces the static stage2_region size in the linker script to zero as it is no longer needed.
These findings show that FlexAlloc is able to successfully receive, use, and handback pages
given by the host for usage exclusively as VM stage-2 page tables.

>>>>

Although the metadata structs have a much smaller memory footprint than the stage-2 page tables,
we designed and partially implemented a fully generalized dynamic allocation interface that
could be used to support dynamic allocation for all metadata structs which we call the
Dynamic Page Manager (DPM). DPM handles all of the work required to receive and return
memory from the hostvisor allowing other "services" in EL2 to exchange memory with DPM using
a very similiar interface to the \textit{alloc\_pages} and \textit{free\_pages} interface available in EL1. We describe
this interface in detail in Section 4.

@@

In order to make sure that the host can reasonably be expected to find 8x 1MB
contiguous regions when booting a VM, we evaluated how many successful
\textit{alloc\_pages(1MB)} calls could be made before failure. To reproduce our tests,
simply compile host-sekvm-project with the \textit{ALLOC\_STRESS\_TEST} macro defined.
Across our three trails, after booting host SeKVM with the FlexAlloc extension,
we were able to achieve between 7049 and 7054 successful 1MB allocations
from \textit{alloc\_pages(1MB)} calls. Since each VM only needs 8 successful allocations,
we believe that the upperbound on the number of VM's due to potential \textit{alloc\_pages(1MB)}
failures is sufficiently high.

We verified the changes in corevisor's memory footprint by checking the number of
pages owned by the corevisor according to the \textit{s2\_pages} array in \textit{el2\_data} at key points
throughout the VM boot and destruction processes. On a host running SeKVM without the
FlexAlloc extension, we observed that the Corevisor owned 65549 pages before booting a VM,
while running a VM, and after destroying a VM. On a host running SeKVM with the FlexAlloc
extension, we observed that the Corevisor owned 32768 pages before VM boot, 34817 pages
during the life of the VM, and 32768 pages after destroying the VM. Note that FlexAlloc also
reduces the static stage2_region size in the linker script to zero as it is no longer needed.
These findings show that FlexAlloc is able to successfully receive, use, and handback pages
given by the host for usage exclusively as VM stage-2 page tables.
